Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
finish adjusting example alignments
No pass by reference?
A paragraph about WBCF (may need to be relocated to section 4)

Together, integrity and confidentiality protect a caller's data until its callee returns
to it. However, it is possible that an intermediate caller is not returned
{\em to}, but rather returned {\em past}, to some ancestor caller! For
example, function $A$ calls function B, which in turn calls $C$, which
returns directly to $A$ by resetting the stack pointer to $A$'s stack frame
and branching to the address after the call from $A$ to $B$.
Strictly speaking, this is not an information-flow problem: the caller's XXXXXX.
\BCP{Still working on this bit.}
But a lower level caller might have been relying on the intermediate
caller to finish its computation, so it is worth protecting control flow even from
attacks that do not violate data protections. We formalize this as {\em return-to-caller}.

@@

>>>>

\BCP{We agreed that most or all of this belongs in Section 4...}Together,
integrity and confidentiality protect a caller's data until its callee
returns to it. However, it is possible that an intermediate caller is not
returned {\em to}, but rather returned {\em past}, to some ancestor caller!
For example, function $A$ calls function $B$, which in turn calls $C$, which
returns directly to $A$ by resetting the stack pointer to $A$'s stack frame
and branching to the address after the call from $A$ to $B$.  Strictly
speaking, this is not an information-flow violation, since neither $A$'s nor
$B$'s stack frames are improperly read or written by $C$.  But it is still
arguably unsafe in general.  For example, suppose that $B$'s continuation
after the call to $C$ takes $C$'s result, doubles it, and returns this to
$A$.  If $A$'s correct behavior after the call to $B$ returns depends on the
result it receives being a even number---i.e., $A$ is trusting that $B$'s
continuation will execute after $C$ returns, perhaps because $A$ and $B$ are
written by the same person while $C$ is an untrusted library---then $C$ can
cause it to behave incorrectly, possibly even insecurely, by returning an
odd result directly to $A$.
%
Thus, a formal definition of safe use of the stack should include the
condition that calls and returns are {\em well bracketed}, e.g., $C$ should
only return to $A$.

@@

\bcp{we probably want to remark that this notion is pretty
much the same as in StkTokens, just formalized a little differently.}
